---
title: "Talks on research data management"
author: "Lennart Wittkuhn"
affiliation: "Max Planck Research Group NeuroCode</br>Max Planck Institute for Human Development</br>Max Planck UCL Centre for Computational Psychiatry and Ageing Research</br>Berlin, Germany"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    self_contained: true
    toc_float: true
    toc_depth: 3
    number_sections: false
    highlight: pygments
    theme: darkly
    code_folding: "hide"
    df_print: paged
    fig_caption: true
fig.align: "center"
---

[![Build Status](https://app.travis-ci.com/lnnrtwttkhn/talk-rdm.svg?branch=master)](https://app.travis-ci.com/lnnrtwttkhn/talk-rdm)
[![License: CC BY-SA 4.0](https://img.shields.io/badge/License-CC%20BY--SA%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by-sa/4.0/)

# Overview 👋

Welcome!

This website hosts the slides and other resources for my talks on research data management, reproducibility and beyond.

The current version of the slides can be found in the [main](#main) section.
Previous versions of the slides can be found in the [archive](#archive) section.
You can find the GitHub repository with all the source code [here](https://github.com/lnnrtwttkhn/talk-rdm).
All contents are licensed under Creative Commons Attribution-ShareAlike 4.0 International Public License (for details, see [here](https://github.com/lnnrtwttkhn/talk-rdm/blob/master/LICENSE) and [here](https://creativecommons.org/licenses/by-sa/4.0/)).
If you notice any issues or have suggestions for improvement, I would be glad to hear from you!
Please open an [issue](https://github.com/lnnrtwttkhn/talk-rdm/issues) on GitHub or contact me via [email](mailto:wittkuhn@mpib-berlin.mpg.de).
Thanks!

```{r, echo=FALSE, message=FALSE}
# allow duplicate labels: https://bookdown.org/yihui/rmarkdown-cookbook/duplicate-label.html
options(knitr.duplicate.label = "allow")
```

```{r, echo=FALSE, message=FALSE}
if (!requireNamespace("pacman")) install.packages("pacman")
packages = c("here", "rmarkdown", "xaringan")
pacman::p_load(char = packages)
```

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_input = here::here("input")
path_public_input = here::here("public", "input")
# copy input folder to public
system2(command = "mkdir", args = "public")
system2(command = "cp", args = sprintf("-r %s %s", path_input, path_public_input))
```

```{r, echo=FALSE, results="hide"}
render_xaringan = function(name, path_rmd){
  path_rmd_copy = here::here("public", paste0(name, ".Rmd"))
  system2(command = "cp", args = sprintf("%s %s", path_rmd, path_rmd_copy))
  name_html = paste0(name, ".html")
  path_html = here::here("public", name_html)
  # render twice because of bibtex (not needed atm):
  xfun::Rscript_call(rmarkdown::render, list(input = path_rmd_copy, output_file = path_html))
  #rmarkdown::render(path_rmd_copy, 'all', output_file = path_html)
  return(name_html)
}
```

```{r, echo=FALSE, results="hide"}
print_list = function(path_html = NULL, path_rmd = NULL, path_notes = NULL){
  repo_url = "https://github.com/lnnrtwttkhn/talk-rdm/blob/master"
  cat(paste0('- <a href="', path_html, '" target="_blank">Slides</a>\n'))
  cat(paste0('- <a href="', file.path(repo_url, path_rmd), '" target="_blank">Source</a>\n'))
  cat(sprintf("- [Notes](%s)\n", path_notes))
}
```

# Main ✨

The current version of the slides is available below:

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_source = "talk-rdm.Rmd"
path_html = render_xaringan(name = "talk-rdm", path_rmd = here::here(path_source))
```

```{r, echo=FALSE, results="asis"}
print_list(path_html = path_html, path_rmd = path_source)
```

```{r, echo=FALSE}
knitr::include_url(path_html)
```

# Archive 📚

## Open Science Ambassadors Day 2021

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5575219.svg)](https://doi.org/10.5281/zenodo.5575219)
[![PDF](https://img.shields.io/badge/PDF-Download-<COLOR>.svg)](https://github.com/lnnrtwttkhn/talk-rdm/releases/download/v2.0/talk-rdm.pdf)

The following slides were presented during a talk prepared for the "Open Science Ambassadors Day 2021" hosted by the [Max Planck PhDnet](https://www.phdnet.mpg.de/home) and the [Max Planck Digital Library](https://www.mpdl.mpg.de/en/) (see details [here](https://osambassadors.mpdl.mpg.de/)) on 18<sup>th</sup> of October 2021.

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
archive_name = "20211018-osambassadors"
path_source = file.path("archive", archive_name, "talk-rdm.Rmd")
path_html = render_xaringan(name = archive_name, path_rmd = here::here(path_source))
```

```{r, echo=FALSE, results="asis"}
print_list(path_html = path_html, path_rmd = path_source)
```

```{r, echo=FALSE}
knitr::include_url(path_html)
```

## Max Planck Digital Library

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5012477.svg)](https://doi.org/10.5281/zenodo.5012477)

The following slides were presented during a talk prepared for the "Discussion Series: Human Research Data in Practice" hosted by the [Max Planck Digital Library](https://www.mpdl.mpg.de/en/) (see details [here](https://rdm.mpdl.mpg.de/2021/05/27/discussion-series-human-research-data-in-practice-on-22th-june-2021/)) on 22<sup>nd</sup> of June 2021.

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
archive_name = "20210622-mpdl"
path_source = file.path("archive", archive_name, "talk-rdm.Rmd")
path_html = render_xaringan(name = archive_name, path_rmd = here::here(path_source))
```

```{r, echo=FALSE, results="asis"}
print_list(path_html = path_html, path_rmd = path_source)
```

```{r, echo=FALSE}
knitr::include_url(path_html)
```

