---
title: "Talks on research data management, open science and reproducibility"
author: "Lennart Wittkuhn"
affiliation: "Max Planck Research Group NeuroCode</br>Max Planck Institute for Human Development</br>Max Planck UCL Centre for Computational Psychiatry and Ageing Research</br>Berlin, Germany"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    self_contained: true
    toc_float: true
    toc_depth: 3
    number_sections: false
    highlight: pygments
    theme: darkly
    code_folding: "hide"
    df_print: paged
    fig_caption: true
fig.align: "center"
---

[![Github Actions](https://github.com/lnnrtwttkhn/talk-rdm/actions/workflows/main.yml/badge.svg)](https://github.com/lnnrtwttkhn/talk-rdm/actions/workflows/main.yml)
[![License: CC BY-SA 4.0](https://img.shields.io/badge/License-CC%20BY--SA%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by-sa/4.0/)

# Overview 👋

Welcome!

This website hosts the slides and other resources for my talks on research data management, reproducibility and beyond.

The current version of the slides can be found in the [main](#main) section.
Previous versions of the slides can be found in the [archive](#archive) section.
You can find the GitHub repository with all the source code [here](https://github.com/lnnrtwttkhn/talk-rdm).
All contents are licensed under Creative Commons Attribution 4.0 International (CC BY 4.0) license (for details, see [here](https://github.com/lnnrtwttkhn/talk-rdm/blob/master/LICENSE) and [here](https://creativecommons.org/licenses/by-sa/4.0/)).
If you notice any issues or have suggestions for improvement, I would be glad to hear from you!
Please open an [issue](https://github.com/lnnrtwttkhn/talk-rdm/issues) on GitHub or contact me via [email](mailto:wittkuhn@mpib-berlin.mpg.de).
Thanks!

```{r, echo=FALSE, message=FALSE}
# allow duplicate labels: https://bookdown.org/yihui/rmarkdown-cookbook/duplicate-label.html
options(knitr.duplicate.label = "allow")
```

```{r, echo=FALSE, message=FALSE}
if (!requireNamespace("pacman")) install.packages("pacman")
packages = c("here", "rmarkdown", "xaringan")
pacman::p_load(char = packages)
```

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_input = here::here("input")
path_public_input = here::here("public", "input")
# copy input folder to public
system2(command = "mkdir", args = "public")
system2(command = "cp", args = sprintf("-r %s %s", path_input, path_public_input))
```

```{r, echo=FALSE, results="hide"}
render_xaringan = function(name, path_rmd){
  path_rmd_copy = here::here("public", paste0(name, ".Rmd"))
  system2(command = "cp", args = sprintf("%s %s", path_rmd, path_rmd_copy))
  name_html = paste0(name, ".html")
  path_html = here::here("public", name_html)
  # render twice because of bibtex (not needed atm):
  xfun::Rscript_call(rmarkdown::render, list(input = path_rmd_copy, output_file = path_html))
  #rmarkdown::render(path_rmd_copy, 'all', output_file = path_html)
  return(name_html)
}
```

```{r, echo=FALSE, results="hide"}
print_list = function(path_html = NULL, path_rmd = NULL, path_notes = NULL){
  repo_url = "https://github.com/lnnrtwttkhn/talk-rdm/blob/master"
  cat(paste0('- <a href="', path_html, '" target="_blank">Slides</a>\n'))
  cat(paste0('- <a href="', file.path(repo_url, path_rmd), '" target="_blank">Source</a>\n'))
  cat(sprintf("- [Notes](%s)\n", path_notes))
}
```

# Main ✨

The current version of the slides is available below:

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_source = "talk-rdm.Rmd"
path_html = render_xaringan(name = "talk-rdm", path_rmd = here::here(path_source))
```

```{r, echo=FALSE, results="asis"}
print_list(path_html = path_html, path_rmd = path_source)
```

```{r, echo=FALSE}
knitr::include_url(path_html)
```

# Archive 📚

## 5<sup>th</sup> RDM-Workshop 2022 on Research Data Management in the Max Planck Society

The following slides were presented during a talk prepared for the [5<sup>th</sup> RDM-Workshop 2022 on Research Data Management in the Max Planck Society](https://rdm.mpdl.mpg.de/2022/05/09/5-fdm-workshop-2022-forschungsdatenmanagement-in-der-max-planck-gesellschaft-call-for-participation/) at the [Max Planck Institute for Human Cognitive and Brain Sciences](https://www.mpib-berlin.mpg.de/en) in Leipzig, Germany from the 13<sup>th</sup> to 14<sup>th</sup> of September 2022.

### Abstract

> Wir bitten um eine kurze Beschreibung des möglichen Beitrags in ca. fünf Sätzen und einen vorläufigen (deutschen) Präsentationstitel.

Vorläufiger Titel: **Forschung als Software Engineering - Lösung für alles?**

Unzureichende Reproduzierbarkeit, mangelnde Transparenz und ineffiziente Arbeitsabläufe - viele wissenschaftliche Disziplinen haben einen großen Innovationsbedarf.
Zudem wird der Forschungsprozess immer digitaler, komputationaler und interaktiver.
In meinem Vortrag argumentiere ich, dass technische Lösungen für diese Herausforderungen bereits vorhanden und in der professionellen Softwareentwicklung zu finden sind.
Dazu zählen vor allem Tools für interaktive Versionskontrolle von Daten wie Git oder DataLad und Software-Container wie Docker.
Ich diskutiere wie diese Tools wissenschaftliche Arbeitsabläufe transformieren und welche (vorranging nicht technischen) Hürden bei ihrer Implementierung bestehen.
Ähnliche vorherige Vorträge finden sich auf https://lennartwittkuhn.com/talk-rdm/.

## Lifespan Neural Dynamics Group

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5586318.svg)](https://doi.org/10.5281/zenodo.5586318)
[![PDF](https://img.shields.io/badge/PDF-Download-<COLOR>.svg)](https://github.com/lnnrtwttkhn/talk-rdm/releases/download/v3.0/talk-rdm.pdf)

The following slides were presented during a talk prepared for the [Lifespan Neural Dynamics Group (LNDG)](https://www.mpib-berlin.mpg.de/research/research-centers/lip/projects/lndg) at the [Max Planck Institute for Human Development](https://www.mpib-berlin.mpg.de/en) on 20<sup>th</sup> of October 2021.

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
archive_name = "20211020-lndg"
path_source = file.path("archive", archive_name, "talk-rdm.Rmd")
path_html = render_xaringan(name = archive_name, path_rmd = here::here(path_source))
```

```{r, echo=FALSE, results="asis"}
print_list(path_html = path_html, path_rmd = path_source)
```

```{r, echo=FALSE}
knitr::include_url(path_html)
```

## Open Science Ambassadors Day 2021

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5575219.svg)](https://doi.org/10.5281/zenodo.5575219)
[![PDF](https://img.shields.io/badge/PDF-Download-<COLOR>.svg)](https://github.com/lnnrtwttkhn/talk-rdm/releases/download/v2.0/talk-rdm.pdf)

The following slides were presented during a talk prepared for the "Open Science Ambassadors Day 2021" hosted by the [Max Planck PhDnet](https://www.phdnet.mpg.de/home) and the [Max Planck Digital Library](https://www.mpdl.mpg.de/en/) (see details [here](https://osambassadors.mpdl.mpg.de/)) on 18<sup>th</sup> of October 2021.

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
archive_name = "20211018-osambassadors"
path_source = file.path("archive", archive_name, "talk-rdm.Rmd")
path_html = render_xaringan(name = archive_name, path_rmd = here::here(path_source))
```

```{r, echo=FALSE, results="asis"}
print_list(path_html = path_html, path_rmd = path_source)
```

```{r, echo=FALSE}
knitr::include_url(path_html)
```

## Max Planck Digital Library

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5012477.svg)](https://doi.org/10.5281/zenodo.5012477)

The following slides were presented during a talk prepared for the "Discussion Series: Human Research Data in Practice" hosted by the [Max Planck Digital Library](https://www.mpdl.mpg.de/en/) (see details [here](https://rdm.mpdl.mpg.de/2021/05/27/discussion-series-human-research-data-in-practice-on-22th-june-2021/)) on 22<sup>nd</sup> of June 2021.

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
archive_name = "20210622-mpdl"
path_source = file.path("archive", archive_name, "talk-rdm.Rmd")
path_html = render_xaringan(name = archive_name, path_rmd = here::here(path_source))
```

```{r, echo=FALSE, results="asis"}
print_list(path_html = path_html, path_rmd = path_source)
```

```{r, echo=FALSE}
knitr::include_url(path_html)
```

### Abstract

**Title:** "Towards a workflow for open and reproducible fMRI studies"

> Achieving computational reproducibility and accessible data sharing can be challenging, in particular for neuroimaging research that involves large amounts of heterogeneous data and code. Here, we showcase a workflow that combines several software tools to allow reproducibility and transparent sharing of code and data of a human fMRI study.

> We recently published an open-access paper (Wittkuhn & Schuck, 2021, Nature Communications) together with the code, data and computational environments needed to reproduce the reported results. We shared > 10 datasets via GIN (G-Node Infrastructure) as modular version-controlled units, including fMRI data organized in BIDS format and derived data, such as pre-processed fMRI data and data quality metrics.

> Research data was version-controlled using DataLad. Following the DataLad YODA principles, we nested datasets as modular units, allowing to better establish data provenance, i.e., a clear overview which code used which input data to produce which output data. Code that reproduced the analyses was integrated with additional documentation using RMarkdown notebooks. The notebooks were automatically executed using continuous integration on GitLab. In this process, data was retrieved from GIN using DataLad, the notebooks were rendered and deployed to a website (https://wittkuhn.mpib.berlin/highspeed/). Code execution was performed using software containers (Docker and Singularity) and virtual environments, allowing to reproduce the computational environment.

**Keywords:** data sharing, reproducibility, open science, version-control, fMRI
